---
title: "Progress Report"
date:  "`r Sys.time()`"
output:
  html_document:
params:
  basename: "33434.log"
  RMD_ARGS: "."
---

# System Information

```{r setup, include = FALSE}
source(paste(params$RMD_ARGS, "rmd_args.R", sep="/"))
```


## Monitored Processes

The following table shows all processes monitored. You may visit other generated reports for information about these processes.

* `TIME`: The time when the process is detected.
* `PID`: Process ID.
* `CMD`: The command line used to start a task.
* `EXE`: Absolute path of the executable.
* `CWD`: The working directory when the process is started. **WARNING**: If a process changes its working directory, it will not be detected!

```{r processes}
reg_filename <- paste0(params$basename, ".reg.tsv")

print_kable(reg_filename)
```

## File System

* `DEVICE`: Corresponding device representation, usually in `/dev`.
* `MOUNT_POINT`: Where this device is mounted.
* `FSTYPE`: Device file system type. e.g. `ntfs`.
* `OPTS`: Device mount options.
* `TOTAL`: Device total space.
* `USED`: How many space is used.

```{r fs}
mnt_filename <- paste0(params$basename, ".mnt.tsv")

print_kable(mnt_filename)
```


## CPU

```{r cpu_fn}
cpu_filename <- paste0(params$basename, ".sys.cpu.tsv")
HAVE_CPU <- file.exists(cpu_filename)
if (HAVE_CPU) {
    cpu_file <- read_tsv(cpu_filename, show_col_types = FALSE) %>%
        dplyr::mutate(TIME = as.POSIXct(TIME, format = record_time_format))

    cpu_gathered_table <- tidyr::gather(cpu_file, key = "CPU_NAME", value = "CPU_PERCENT", -TIME)

    lvls <- cpu_file$TIME
    HAVE_CPU <- length(lvls) != 0
}
if (!HAVE_CPU) {
    print_se()
}
```

The following graph shows the CPU percentage per logical processor.

e.g. For a CPU supporting "4 cores 8 threads", there should be 8 logical processors so 8 lines.

```{r cpu_logical, eval = HAVE_CPU}
g <- ggplot(cpu_gathered_table) +
    geom_area(aes(x = TIME, y = CPU_PERCENT, fill = CPU_NAME, group = CPU_NAME))
cpu_graph_prettify(g)
```


The following graph shows mean CPU utilization among all logical processors. If there are less than 120 events, this graph would be consisted with a single solid blue line, indicating mean CPU utilization. If there are more than 120 events, all events would be grouped into 40 groups and a boxplot will be displayed. Blue dotted line is real mean CPU utilization and the red line is the mean of mean CPU utilization within a group. Using this method, it would be more efficient to see the trend.

```{r cpu_mean, eval = HAVE_CPU}
cpu_total <- cpu_gathered_table %>%
    dplyr::group_by(TIME) %>%
    dplyr::summarise(SUM = sum(CPU_PERCENT))
scale_by <- as.integer(length(lvls) / MAX_X_LABS)
cpu_total <- cpu_total %>%
    dplyr::mutate(BREAK_TIME = TIME[as.integer(row_number() / scale_by) * scale_by + 1])
if (scale_by >= 3) {
    g <- ggplot(cpu_total, aes(x = BREAK_TIME, y = SUM)) +
        geom_boxplot(
            aes(group = BREAK_TIME),
            outlier.alpha = 0,
            width = scale_by
        ) +
        geom_line(
            aes(x = TIME, y = SUM),
            group = 1,
            color = "blue",
            linetype = "dotted"
        ) +
        stat_summary(fun = mean, geom = "line", aes(group = 1), color = "red") +
        stat_summary(fun = mean, geom = "point", color = "red")
} else {
    g <- ggplot(cpu_total) +
        geom_line(aes(x = TIME, y = SUM), group = 1, color = "blue")
}
cpu_graph_prettify(g)
```

## Memory

```{r mem_fn}
mem_filename <- paste0(params$basename, ".sys.mem.tsv")
HAVE_MEM <- file.exists(mem_filename)
mem_col_spec <- list(
    TIME = col_character(),
    TOTAL = col_number(),
    USED = col_number(),
    BUFFERED = col_number(),
    CACHED = col_number(),
    SHARED = col_number()
)
if (HAVE_MEM) {
    mem_file <- read_tsv(mem_filename, col_types = mem_col_spec) %>%
        dplyr::mutate(TIME = as.POSIXct(TIME, format = record_time_format))
    mem_gathered_table <- tidyr::gather(mem_file, key = "MEM_NAME", value = "MEM_USED", -TIME)
    HAVE_MEM <- length(mem_file$TIME) != 0
}
if (!HAVE_MEM) {
    print_se()
}
```

The following graph shows system memory information.

* `TOTAL`: Total available *PHYSICAL* memory, excluding SWAP.
* `USED`: None-Zero memory.
* `CLAIMED`: `TOTAL` - `AVAIL`. `AVAIL` is an estimation of physical memory available for starting new applications, without swapping.
* `BUFFER`: Cache for things like file system metadata.
* `CACHED`: Cache for various things.
* `SHARED`: A subset of resident memory (RES) that may be used by other processes. It will include shared anonymous pages and shared file-backed pages. It also includes private pages mapped to files representing program images and shared libraries.

```{r mem, eval = HAVE_MEM}
ggplot(mem_gathered_table) +
    geom_line(aes(x = TIME, y = MEM_USED, color = MEM_NAME, group = MEM_NAME)) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90)) +
    scale_x_datetime(
        "Time",
        breaks = breaks_pretty(n = MAX_X_LABS),
        labels = label_date(format = record_time_format)
    ) +
    scale_y_continuous(
        "Memory Allocated",
        breaks = scales::breaks_extended(n = MAX_X_LABS),
        labels = scales::label_bytes(units = "auto_binary", accuracy = 0.01),
        limits = c(0, NA)
    ) +
    labs(title = "Mean Memory Ultilization plot")
```

## SWAP

```{r swap_fn}
swap_filename <- paste0(params$basename, ".sys.swap.tsv")
HAVE_SWAP <- file.exists(swap_filename)
swap_col_spec <- list(
    TIME = col_character(),
    TOTAL = col_number(),
    USED = col_number()
)
if (HAVE_SWAP) {
    swap_file <- read_tsv(swap_filename, col_types = swap_col_spec) %>%
        dplyr::mutate(TIME = as.POSIXct(TIME, format = record_time_format))
    swap_gathered_table <- tidyr::gather(swap_file, key = "SWAP_NAME", value = "SWAP_USED", -TIME)
    HAVE_SWAP <- length(swap_file$TIME) != 0
}
if (!HAVE_SWAP) {
    print_se()
}
```

SWAP is the formerly resident portion of a task's address space written to the swap file when physical memory becomes overcommitted.

* `TOTAL`: Total available SWAP.
* `USED`: Used SWAP.


```{r swap, eval = HAVE_SWAP}
ggplot(swap_gathered_table) +
    geom_line(aes(x = TIME, y = SWAP_USED, color = SWAP_NAME, group = SWAP_NAME)) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90)) +
    scale_x_datetime(
        "Time",
        breaks = breaks_pretty(n = MAX_X_LABS),
        labels = label_date(format = record_time_format)
    ) +
    scale_y_continuous(
        "SWAP Allocated",
        breaks = scales::breaks_extended(n = MAX_X_LABS),
        labels = scales::label_bytes(units = "auto_binary", accuracy = 0.01),
        limits = c(0, NA)
    ) +
    labs(title = "Mean Memory Ultilization plot")
```


## STDOUT

The standard output. If the process is not initialized by `python -m proc CMD`, this field would be blank.

```{r stdout}
print_file(paste0(params$basename, ".stdout.log"))
```

## STDERR

The standard error, similar to STDOUT section.

```{r stderr}
print_file(paste0(params$basename, ".stderr.log"))
```


## Help

* Manpage of Unix command `top`: <https://www.man7.org/linux/man-pages/man1/top.1.html>
* Documentation of Python package `psutil`: <https://psutil.readthedocs.io/en/latest/>
* Manpage of Process FileSystem: <https://man7.org/linux/man-pages/man5/proc.5.html>
